Effect of character correlation

### 2019-05-31 Analysis/01-EffectCorrelationStats.Rmd
Updated figures and tables

```{r, warning = FALSE}
## Summarise into a table
scenario_list <- list(scenario_RF_norm, scenario_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(scenario_list, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_scen_test <- paste("Difference between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correction)")

@@

```{r, warning = FALSE}
## Summarise into a table
character_list <- list(character_RF_norm, character_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(character_list, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_char_test <- paste("Difference between the pooled number of characters. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, warning = FALSE}
## Summarise into a table
taxa_list <- list(taxa_RF_norm, taxa_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(taxa_list, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_tax_test <- paste("Difference between the pooled number of taxa. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm)
metric.labels <- c("RF", "Tr")
test_table <- pair.test.table(methods_list, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_met_test <- paste("Difference between the pooled methods. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

>>>>

```{r, warning = FALSE}
## Summarise into a table
scenario_list <- list(scenario_RF_norm, scenario_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(scenario_list, metric.label = metric.labels)
## Change the ":" into vs.
test_table$test <- gsub(":", " vs. ", test_table$test)
```

```{r, echo = FALSE}
## Caption
cap_pool_scen_test <- paste("Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for each minimised (mini), maximised (maxi) and randomised (rand) character differences. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).")

@@

```{r, warning = FALSE}
## Summarise into a table
character_list <- list(character_RF_norm, character_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(character_list, metric.label = metric.labels)
## Change the ":" into vs.
test_table$test <- gsub(":", " vs. ", test_table$test)
```

```{r, echo = FALSE}
## Caption
cap_pool_char_test <- paste("Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for the three different number of characters: 100 (c100), 350 (c350) and 1000 (c1000). Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).")

@@

```{r, warning = FALSE}
## Summarise into a table
taxa_list <- list(taxa_RF_norm, taxa_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(taxa_list, metric.label = metric.labels)
## Change the ":" into vs.
test_table$test <- gsub(":", " vs. ", test_table$test)
```

```{r, echo = FALSE}
## Caption
cap_pool_tax_test <- paste("Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for the three different number of taxa: 25 (t25), 75 (t75) and 150 (t150). Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).")

@@

```{r, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm)
metric.labels <- c("RF", "Tr")
test_table <- pair.test.table(methods_list, metric.label = metric.labels)
## Change the ":" into vs.
test_table$test <- gsub(":", " vs. ", test_table$test)
```

```{r, echo = FALSE}
## Caption
cap_pool_met_test <- paste("Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for the two different inference methods: bayesian or maximum parsimony. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).")

### 2019-05-31 Analysis/02-EffectCorrelationFullResults.Rmd
Updated figures and tables

```{r, warning = FALSE, warning = FALSE}
## Summarise into a table
scenario_list <- list(scenario_RF_norm, scenario_Tr_norm, scenario_RF_null, scenario_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(scenario_list, comp.label = comp.labels, metric.label = metric.labels)
```

@@

```{r, warning = FALSE}
## Summarise into a table
character_list <- list(character_RF_norm, character_Tr_norm, character_RF_null, character_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(character_list, comp.label = comp.labels, metric.label = metric.labels)
```

@@

```{r, warning = FALSE}
## Summarise into a table
taxa_list <- list(taxa_RF_norm, taxa_Tr_norm, taxa_RF_null, taxa_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(taxa_list, comp.label = comp.labels, metric.label = metric.labels)
```

@@

```{r, warning = FALSE, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm, method_RF_null, method_Tr_null)
comp.labels <- c("Best", rep("", 1), "Null", rep("", 1))
metric.labels <- rep(c("RF", "Tr"), 2)
test_table <- pair.test.table(methods_list, comp.label = comp.labels, metric.label = metric.labels)
```

>>>>

```{r, warning = FALSE, warning = FALSE}
## Summarise into a table
scenario_list <- list(scenario_RF_norm, scenario_Tr_norm, scenario_RF_null, scenario_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(scenario_list, comp.label = comp.labels, metric.label = metric.labels)
## Change the ":" into vs.
test_table$test <- gsub(":", " vs. ", test_table$test)
```

@@

```{r, warning = FALSE}
## Summarise into a table
character_list <- list(character_RF_norm, character_Tr_norm, character_RF_null, character_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(character_list, comp.label = comp.labels, metric.label = metric.labels)
## Change the ":" into vs.
test_table$test <- gsub(":", " vs. ", test_table$test)
```

@@

```{r, warning = FALSE}
## Summarise into a table
taxa_list <- list(taxa_RF_norm, taxa_Tr_norm, taxa_RF_null, taxa_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(taxa_list, comp.label = comp.labels, metric.label = metric.labels)
## Change the ":" into vs.
test_table$test <- gsub(":", " vs. ", test_table$test)
```

@@

```{r, warning = FALSE, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm, method_RF_null, method_Tr_null)
comp.labels <- c("Best", rep("", 1), "Null", rep("", 1))
metric.labels <- rep(c("RF", "Tr"), 2)
test_table <- pair.test.table(methods_list, comp.label = comp.labels, metric.label = metric.labels)
## Change the ":" into vs.
test_table$test <- gsub(":", " vs. ", test_table$test)
```

### 2019-05-31 Analysis/03-EffectCorrelationFigure.Rmd
Updated figures and tables

```{r, fig.width=12, fig.height=12}
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 2, what = "best",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "NTS(RF) for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "best", ylab = "NTS(RF) for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "best",
    ylab = "NTS(RF) for 150 taxa", NTS = TRUE)
par(op)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/RF_results_best.pdf",width = 8,height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 2, what = "best",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "NTS(RF) for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "best", ylab = "NTS(RF) for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "best",
    ylab = "NTS(RF) for 150 taxa", NTS = TRUE)
par(op)
# dev.off()
```

@@

```{r, fig.width=12, fig.height=12}
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 4, what = "best",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "NTS(Tr) for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "best", ylab = "NTS(Tr) for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "best",
    ylab = "NTS(Tr) for 150 taxa", NTS = TRUE)
par(op)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/Tr_results_best.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 4, what = "best",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "NTS(Tr) for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "best", ylab = "NTS(Tr) for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "best",
    ylab = "NTS(Tr) for 150 taxa", NTS = TRUE)
par(op)
# dev.off()
```

@@

```{r, fig.width=12, fig.height=12}
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 2, what = "null",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "NTS(RF) for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "null", ylab = "NTS(RF) for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "null",
    ylab = "NTS(RF) for 150 taxa", NTS = TRUE)
par(op)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/RF_results_null.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 2, what = "null",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "NTS(RF) for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "null", ylab = "NTS(RF) for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "null",
    ylab = "NTS(RF) for 150 taxa", NTS = TRUE)
par(op)
# dev.off()
```

@@

```{r, fig.width=12, fig.height=12}
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 4, what = "null",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "NTS(Tr) for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "null", ylab = "NTS(Tr) for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "null",
    ylab = "NTS(Tr) for 150 taxa", NTS = TRUE)
par(op)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/Tr_results_null.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 4, what = "null",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "NTS(Tr) for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "null", ylab = "NTS(Tr) for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "null",
    ylab = "NTS(Tr) for 150 taxa", NTS = TRUE)
par(op)
# dev.off()
```

>>>>

```{r, fig.width=12, fig.height=12}
op <- par(mfrow=c(3,1), mar = c(2, 5, 1, 2))
plot.results.single(t25_list, metric = 2, what = "best",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "best", ylab = "Robinson-Foulds Normalised Tree Similarity\n75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "best",
    ylab = "150 taxa", NTS = TRUE)
par(op)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/RF_results_best.pdf",width = 8,height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 5, 1, 2))
plot.results.single(t25_list, metric = 2, what = "best",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "best", ylab = "Robinson-Foulds Normalised Tree Similarity\n75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "best",
    ylab = "150 taxa", NTS = TRUE, legend = TRUE, leg.pos = "bottomright", leg.cex = 1.1)
par(op)
# dev.off()
```

@@

```{r, fig.width=12, fig.height=12}
op <- par(mfrow=c(3,1), mar = c(2, 5, 1, 2))
plot.results.single(t25_list, metric = 4, what = "best",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "best", ylab = "Triplets Normalised Tree Similarity\n75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "best",
    ylab = "150 taxa", NTS = TRUE, legend = TRUE, leg.pos = "bottomright", leg.cex = 1.1)
par(op)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/Tr_results_best.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 5, 1, 2))
plot.results.single(t25_list, metric = 4, what = "best",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "best", ylab = "Triplets Normalised Tree Similarity\n75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "best",
    ylab = "150 taxa", NTS = TRUE, legend = TRUE, leg.pos = "bottomright", leg.cex = 1.1)
par(op)
# dev.off()
```

@@

```{r, fig.width=12, fig.height=12}
op <- par(mfrow=c(3,1), mar = c(2, 5, 1, 3))
plot.results.single(t25_list, metric = 2, what = "null",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "null", ylab = "Robinson-Foulds Normalised Tree Similarity\n75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "null",
    ylab = "150 taxa", NTS = TRUE)
par(op)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/RF_results_null.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 5, 1, 2))
plot.results.single(t25_list, metric = 2, what = "null",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "null", ylab = "Robinson-Foulds Normalised Tree Similarity\n75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "null",
    ylab = "150 taxa", NTS = TRUE)
par(op)
# dev.off()
```

@@

```{r, fig.width=12, fig.height=12}
op <- par(mfrow=c(3,1), mar = c(2, 5, 1, 2))
plot.results.single(t25_list, metric = 4, what = "null",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "null", ylab = "Triplets Normalised Tree Similarity\n75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "null",
    ylab = "150 taxa", NTS = TRUE)
par(op)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/Tr_results_null.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 5, 1, 2))
plot.results.single(t25_list, metric = 4, what = "null",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "null", ylab = "Triplets Normalised Tree Similarity\n75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "null",
    ylab = "150 taxa", NTS = TRUE)
par(op)
# dev.off()
```
